### 2013-11-07 inst/examples/policycosts/writeup.Rmd
writeup updated
combine code and text

```{r cache-options, include=FALSE}
opts_chunk$set(cache=TRUE, cache.path="writeup/")
```

@@

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(dev.args=list(bg="transparent"),
               tidy=FALSE, comment=NA, message=FALSE, warning=FALSE)
theme_notebook <- theme_grey() + 
                  theme(plot.background = 
                          element_rect(fill = "transparent",colour = NA),
                        panel.grid.minor = 
                          element_line(colour = "transparent"))
theme_set(theme_notebook)
```

@@

``` {r fees}
L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
free_increase <- function(c2) function(h, h_prev)  c2 * abs(pmin(h - h_prev, 0)) # increasing harvest is free
free_decrease <- function(c2) function(h, h_prev)  c2 * pmax(h - h_prev, 0) # decreasing harvest is free
fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
none <- function(h, h_prev)  0
penaltyfns <- list(L2=L2, L1=L1, free_decrease=free_decrease, fixed=fixed, free_increase=free_increase)
````

@@

``` {r npv-plot, dependson="quadcosts"}
npv0 <- max(fees$L1) # all have same max, at c2=0 
npv0
fees <- data.frame(c2=c2,fees)
fees <- melt(fees, id="c2")
ggplot(fees, aes(c2, value, col=variable)) + geom_point() + geom_line()
````

@@

```{r print_npv, dependson="apples"}
setkey(dt_npv, variable)
values <- apply(index, 1, function(x) dt_npv[x[1], ][as.integer(x[2]), ]$value)

percent.error <- (values - ((1-reduction)*npv0)) / ((1-reduction)*npv0)* 100

print_npv <- data.frame(model=index$variable, "value realized"=values, 
                        "percent of npv0" = 100*values/npv0, "percent error"=percent.error)

@@

```{r npv_table, dependson="print_npv"} 
library(xtable)
print(xtable(print_npv), type="html")
#pandoc.table(print_npv)
```

@@

``` {r policynames}
L2_policy <- policies$L2[[apples_index["L2"]]]$D
L1_policy <- policies$L1[[apples_index["L1"]]]$D
fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
free_increase_policy <- policies$free_increase[[apples_index["free_increase"]]]$D
free_decrease_policy <- policies$free_decrease[[apples_index["free_decrease"]]]$D
quad_policy <- policies$quad[[apples_index["quad"]]]$D
```

``` {r simulate_policy, dependson=c("policynames", "apples")}
quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"])

reps <- 1:100
names(reps) = paste("rep", 1:10, sep="_")
sims <- list(
  L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed)), 
  L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed)),
  fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed))

@@

```{r }
sims_free <- list(
  L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=none, seed=seed)), 
  L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=none, seed=seed)),
  fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=none, seed=seed))
)
````

@@

error_costs

@@

```{r error_costs_table} 
print(xtable(error_costs), type="html")
#pandoc.table(print_npv)
```

@@

```{r p1, dependson="tidy", fig.width=12}
p1 <- ggplot(dt) +
  geom_line(aes(time, alternate), col="grey20", lwd=1) +
  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + facet_wrap(~penalty_fn) + 
  labs(x="time", y="stock size", title = "Stock Dynamics")
p1
```

```{r Figure3, dependson="tidy", fig.width=12}
p2 <- ggplot(dt) +
  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
  facet_wrap(~penalty_fn) + 
  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
p2
````

@@

quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"]) 
sims <- lapply(1:50, function(reps) list(
  L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L1(apples["L1"])), 
  L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L2(apples["L2"])),
  fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=fixed(apples["fixed"])),
  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_increase_policy, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_increase(apples["increase"])),
  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_decrease_policy, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"])),
  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            quad_policy, z_g, z_m, z_i, 
                            opt$D, profit=quad_profit, penalty= none)
  ))

@@

```{r Figure4}
Fig4a <- ggplot(harvest_trends, 
                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")

Fig4b <- ggplot(harvest_trends, 
                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")
Fig4a
Fig4b
````

@@

FigS4a <- ggplot(fishstock_trends, 
                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")

FigS4b <- ggplot(fishstock_trends, 
                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")
FigS4a
FigS4b
```

>>>>

```{r cache-options, include=FALSE}
opts_chunk$set(cache=TRUE, cache.path="writeup/")
opts_knit$set(upload.fun=socialR::flickr.url)
```

@@

```{r graphing-options, include=TRUE}
opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(dev.args=list(bg="transparent"),
               tidy=FALSE, comment=NA, message=FALSE, warning=FALSE)
opts_chunk$set(echo=FALSE)
theme_set(theme_bw())
```

@@

``` {r fees}
L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
none <- function(h, h_prev)  0
penaltyfns <- list(L2=L2, L1=L1, fixed=fixed)
````

@@

``` {r npv-plot, dependson="quadcosts"}
npv0 <- max(fees$L1) # all have same max, at c2=0 
npv0
fees <- data.frame(c2=c2,fees)
fees <- melt(fees, id="c2")

fees <- subset(fees, variable %in% c("L1", "L2", "fixed"))
ggplot(fees, aes(c2, value, col=variable)) + geom_point() + geom_line()
````

@@

```{r print_npv, dependson="apples"}
setkey(dt_npv, variable)
values <- apply(index, 1, function(x) dt_npv[x[1], ][as.integer(x[2]), ]$value)
percent.error <- (values - ((1-reduction)*npv0)) / ((1-reduction)*npv0)* 100
print_npv <- data.frame(model=index$variable, "value realized"=values, 
                        "percent of npv0" = 100*values/npv0, "percent error"=percent.error)

@@

```{r npv_table, dependson="print_npv", results='asis'} 
library(xtable)
print(xtable(print_npv), type="html")
#pandoc.table(print_npv)
```

@@

``` {r policynames}
L2_policy <- policies$L2[[apples_index["L2"]]]$D
L1_policy <- policies$L1[[apples_index["L1"]]]$D
fixed_policy <- policies$fixed[[apples_index["fixed"]]]$D
```

``` {r simulate_policy, dependson=c("policynames", "apples")}

reps <- 1:100
names(reps) = paste("rep", 1:length(reps), sep="_") # treat as a factor
seeds <- 1:100

sims <- list(
  L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seeds[x])), 
  L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seeds[x])),
  fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seeds[x]))

@@

```{r }
sims_free <- list(
  L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=none, seed=seeds[x])), 
  L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=none, seed=seeds[x])),
  fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=none, seed=seeds[x]))
)
````

@@

cbind(error_costs, sigma_g = sigma_g, reduction = reduction)

@@

```{r error_costs_table, results='asis'} 
print(xtable(error_costs), type="html")
#pandoc.table(print_npv)
```

@@

```{r p1, dependson="tidy", fig.width=12}
p1 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
  geom_line(aes(time, alternate), col="grey20", lwd=1) +
  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + 
  facet_grid(replicate~penalty_fn) + 
  labs(x="time", y="stock size", title = "Stock Dynamics")
p1
```

```{r Figure3, dependson="tidy", fig.width=12}
p2 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
  facet_grid(replicate~penalty_fn) + 
  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
p2
````

@@

quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"]) 
sims <- lapply(1:50, function(reps) list(
  L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L1(apples["L1"])), 
  L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L2(apples["L2"])),
  fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=fixed(apples["fixed"]))
#  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
#                            free_increase_policy, z_g, z_m, z_i, 
#                            opt$D, profit=profit, penalty= free_increase(apples["increase"])),
#  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
#                            free_decrease_policy, z_g, z_m, z_i, 
#                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"])),
#  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
#                            quad_policy, z_g, z_m, z_i, 
#                            opt$D, profit=quad_profit, penalty= none)
  ))

@@

```{r Figure4}
Fig4a <- ggplot(harvest_trends, 
                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + 
  xlab("Fraction of NPV lost to costs") +
  scale_x_continuous(limits=c(0, 0.4))

Fig4b <- ggplot(harvest_trends, 
                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")+
  scale_x_continuous(limits=c(0, 0.4)) 
Fig4a
Fig4b
````

@@

FigS4a <- ggplot(fishstock_trends, 
                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")+
  scale_x_continuous(limits=c(0, 0.4))

FigS4b <- ggplot(fishstock_trends, 
                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs") +
  scale_x_continuous(limits=c(0, 0.4)) 
FigS4a
FigS4b
```
